Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-17 07_Publication_wireframe_and_8Questions.Rmd
Rename file to maintain order to the book

## Who are the intended readers? - list 3 to 5 of them by name  
   * Adam Sparks – disease modeler  
   * Levente Kiss – Powdery mildew taxonomist  
   * Lisa Kelly – Plant pathologist  
   * Paul MacIntosh – Mungbean/ pulse agronomist  
   * Ross Pomroy – Agronomist  
   * Jean Galloway – Plant disease modeller  
   * Art Diggle – Plant disease modeller

>>>>

## Who are the intended readers? - list 3 to 5 of them by name  
   * Adam Sparks – disease modeller  
   * Levente Kiss – Powdery mildew taxonomist  
   * Lisa Kelly – Plant pathologist  
   * Paul MacIntosh – Mungbean/ pulse agronomist  
   * Ross Pomroy – Agronomist  
   * Jean Galloway – Plant disease modeller  
   * Art Diggle – Plant disease modeller
